Token-level author diarization using clustering of stylistic contexts

### 2017-06-01 paper/paper.tex
Send this to Milan

% TODO: replace model A with Model A, for B as well
% TODO: replace $n$-gram and \emph{n}-gram with n-gram, as it is common in literature
% TODO: hange bi-grams to bigrams and tri-grams to trigrams
% TODO: suggestion: remove \texttt-s 
% TODO: change \texit-s ti \emph-s
% TODO: explain BFE training in The proposed approach
% TODO: convert Related work to present

@@

\begin{table}
	\caption{Basic characteristics of training datasets. * represents that there is a true author and plagiarism segments which don't have to originate from a single author.}
	\label{tab:dataset-characteristics}
	\begin{center}
		\begin{tabular}{cccc}
			\toprule
			Task & \thead{Number of \\ documents} & \thead{Average \\ length (in tokens)} & \thead{(min, max)\\authors} \\
			\midrule
			Task \emph{a} & 71 & 1679 & (2, 2)*\\
			Task \emph{b} & 55 & 3767 & (2, 10)\\
			Task \emph{c} & 54 & 3298 & (2, 10)\\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table}

@@

For each of the three subtasks a training dataset is publicly available\footnotemark[1]. \citet{rosso-2016} explain that they are collections of various documents which are part of Webis-TRC-12 dataset \citep{potthast-2013}. Every document in that dataset is constructed from texts of various search results (i.e. authors) for one of the 150 topics in total. By varying different parameters such as the number and proportion of the authors, places in a document where an author switch occurs (between words, sentences or paragraphs), three training and test datasets were generated \citep{rosso-2016}. Test datasets are currently not publicly available and we could not use them for evaluation of our approach. Some basic characteristics of the training datasets are shown in Table \ref{tab:dataset-characteristics}.

@@

We develop two variants of our model which we will refer to as \emph{Model A} and \emph{Model B}. They are mainly differentiated by the the training of the basic feature extractor and feature transformation and in the feature transformation. Model B utilizes a trainable feature transformation that requires a fixed basic feature space. Therefore, the basic feature extractor must be trained on the trained on the whole training dataset. Conversely, Model A's basic feature transformation can be trained specifically allowing for use of less more important features, but it can't use a feature transformation trainable on multiple documents. In both approaches basic features are extracted from a sliding window which moves from token to token and includes the context of each token.

@@

The \emph{compactness loss} $L_\mathrm{c}$ is a weighted sum of within-group variances. The \emph{segregation loss}  $L_\mathrm{s}$ is proportional to the sum of magnitudes (not magnitude of the sum) of forces between $c$ equally charged particles each located at one of the centroids. By minimizing the average loss (the error) across all documents in the training dataset with respect to the parameters of the transformation $\vect{\theta}_T$ we hope to benefit the clustering algorithm. Instead of squared $L^2$ distance, some other distance measure may be used. Also, the way of combining the two losses was somewhat arbitrarily chosen as well as the segregation loss. For the transformation $T$ we have tried a nonlinear transformations represented as neural networks with one or more hidden layers. We didn't explore nonlinear transformations much because they were slower and didn't give as good results as a linear transformation or an elementwise linear transformation:

@@

repo link

For experiments, we used the three PAN 2016 training datasets. The test datasets used in the competition have not been made publicly available. Therefore, our evaluation results might be only moderately comparable to the results of other systems.

@@

\subsection{Experimental setup}
In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}. Model A covered all three tasks and had a several hyperparameters in each: context size, clustering algorithm and its hyperparameters.

Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection. We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values. The best result for task \emph{a} was $cs_a=16$ and for task \emph{b} $cs_b=140$. For task \emph{c}, we left $cs_c=140$ as for task \emph{b}. This hyperparameter probably depends on document's length to a certain extent. If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs. $16, 140, 140$). Although we tested different context size values again on a train set after optimal clustering algorithm selection and obtained no difference in results on a test set, they are probably biased to a certain extent.

For clustering algorithm selection we used manual search over several algorithms. We split the whole dataset into a training and a test set. For each algorithm we were examining, a grid search of its hyperparameters was performed on the train set. We selected an algorithm and hyperparameters that achieved the best performance on a train set (since this is an unsupervised approach), and reported a final performance on the test set.

\paragraph{Model B.} For Model B, we have decided to use choose a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words). The length of the sliding window is set to $120$ characters. Model B uses k-means clustering. We have chosen two trainable feature transformations: linear and elementwise linear. For the both transformations $5\times 10^{-4}$ was chosen for the learning rate. All the hyperparameters are selected manually by  experimenting on the development dataset (approximately $70\%$ of the available dataset). $70\%$ of the development set was used for training basic feature extractors and the transformation. Considering the results on the   validation part of the development set, not very large numbers of iterations seem to be more beneficial. A number of $40$ iterations was chosen for the linear transformation, and $20$ for the elementwise linear transformation. For the output dimension of the linear transformation we have chosen $n_\mathrm{t}=40$, though not much different results seem to be archivable using smaller numbers like $20$, making training and clustering faster.

@@

@@

\subsection{Intrinsic plagiarism detection}

setup
results
don't forget to describe tolerance

\subsection{Author diarization with known numbers of authors}

setup

\subsection{Author diarization with unknown numbers of authors}

setup

\paragraph{Segmentation generation.} something short

features

differences: fixed features + transformation vs document-dependent features

>>>>

% TODO: replace model A with Model A, for B as well
% TODO: replace $n$-gram and \emph{n}-gram with n-gram, as it is common in literature
% TODO: hange bi-grams to bigrams and tri-grams to trigrams
% TODO: suggestion: remove \texttt-s 
% TODO: change \texit-s ti \emph-s
% TODO: explain BFE training in The proposed approach
% TODO: consistency: use only "training set" and "test set" (not dataset, not train) (https://en.wikipedia.org/wiki/Test_set)
% TODO: convert Related work to present

@@

\begin{table}
	\caption{Basic characteristics of training sets. * represents that there is a true author and plagiarism segments which don't have to originate from a single author.}
	\label{tab:dataset-characteristics}
	\begin{center}
		\begin{tabular}{cccc}
			\toprule
			Task & \thead{Number of \\ documents} & \thead{Average \\ length (in tokens)} & \thead{(min, max)\\authors} \\
			\midrule
			Task \emph{a} & 71 & 1679 & (2, 2)*\\
			Task \emph{b} & 55 & 3767 & (2, 10)\\
			Task \emph{c} & 54 & 3298 & (2, 10)\\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table}

@@

For each of the three subtasks a training set is publicly available\footnotemark[1]. \citet{rosso-2016} explain that they are collections of various documents which are part of Webis-TRC-12 dataset \citep{potthast-2013}. Every document in that dataset is constructed from texts of various search results (i.e. authors) for one of the 150 topics in total. By varying different parameters such as the number and proportion of the authors, places in a document where an author switch occurs (between words, sentences or paragraphs), three training and test sets were generated \citep{rosso-2016}. Test datasets are currently not publicly available and we could not use them for evaluation of our approach. Some basic characteristics of the training sets are shown in Table \ref{tab:dataset-characteristics}.

@@

We develop two variants of our model which we will refer to as \emph{Model A} and \emph{Model B}. They are mainly differentiated by the the training of the basic feature extractor and feature transformation and in the feature transformation. Model B utilizes a trainable feature transformation that requires a fixed basic feature space. Therefore, the basic feature extractor must be trained on the trained on the whole training set. Conversely, Model A's basic feature transformation can be trained specifically allowing for use of less more important features, but it can't use a feature transformation trainable on multiple documents. In both approaches basic features are extracted from a sliding window which moves from token to token and includes the context of each token.

@@

The \emph{compactness loss} $L_\mathrm{c}$ is a weighted sum of within-group variances. The \emph{segregation loss}  $L_\mathrm{s}$ is proportional to the sum of magnitudes (not magnitude of the sum) of forces between $c$ equally charged particles each located at one of the centroids. By minimizing the average loss (the error) across all documents in the training set with respect to the parameters of the transformation $\vect{\theta}_T$ we hope to benefit the clustering algorithm. Instead of squared $L^2$ distance, some other distance measure may be used. Also, the way of combining the two losses was somewhat arbitrarily chosen as well as the segregation loss. For the transformation $T$ we have tried a nonlinear transformations represented as neural networks with one or more hidden layers. We didn't explore nonlinear transformations much because they were slower and didn't give as good results as a linear transformation or an elementwise linear transformation:

@@

repo link - move from Ivan1024 to an organization

For experiments, we have used the three PAN 2016 training sets. The test sets used in the competition have not been made publicly available. Therefore, our evaluation results might be only moderately comparable to the results of other systems.

@@

\subsection{Experimental setup}
In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}. Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and its hyperparameters.

Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection. We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values. The best result for task \emph{a} was $cs_a=16$ and for task \emph{b} $cs_b=140$. For task \emph{c}, we left $cs_c=140$ as for task \emph{b}. This hyperparameter probably depends on document's length to a certain extent. If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs. $16, 140, 140$). Although we tested different context size values again on a training set after optimal clustering algorithm selection and obtained no difference in results on a test set, they are probably biased to a certain extent.

For clustering algorithm selection we used manual search over several algorithms. We split the whole dataset into a training and a test set. For each algorithm we were examining, a grid search of its hyperparameters was performed on the training set. We selected an algorithm and hyperparameters that achieved the best performance on a training set (since this is an unsupervised approach), and reported a final performance on the test set.

\paragraph{Model B.} For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words). The length of the sliding window is set to $120$ characters. Model B uses k-means clustering. We have chosen two trainable feature transformations: linear and elementwise linear. For the both transformations $5\times 10^{-4}$ was chosen for the learning rate. All the hyperparameters are selected manually by  experimenting on the development dataset, which is approximately $70\%$ of the available dataset. $70\%$ of the development set was used for training basic feature extractors and the transformation. Considering the results on the   validation part of the development set, not very large numbers of iterations seem to be more beneficial. A number of $40$ iterations was chosen for the linear transformation, and $20$ for the elementwise linear transformation. For the output dimension of the linear transformation we have chosen $n_\mathrm{t}=40$, though not much different results seem to be archivable using smaller numbers like $20$, making training and clustering faster.

@@

don't forget to describe tolerance

@@
